KIN: A method to infer relatedness from low-coverage ancient DNA

### 2022-09-11 paper_overleaf/KIN_a_method_to_estimate_relatedness_from_low_coverage_data_supplements.tex
Updates from Overleaf

\begin{figure}[h]
    \centering
    \includegraphics[width=18cm]{supplementary_info/plots/contam_missspecification.png}
    \caption{False positive and true positive rates as a function of incorrect contamination estimates provided to the ROH-HMM. Dashed vertical line represents true contamination (2.5\%) in simulations, and dotted horizontal line in top panel represents $5\%$ false positive rate.}
    \label{figS10:cnt}
\end{figure}

>>>>

\begin{figure}[h]
    \centering
    \includegraphics[width=18cm]{supplementary_info/plots/contam_missspecification.png}
    \caption{False positive and true positive rates as a function of incorrect contamination estimates provided to the ROH-HMM. Dashed vertical line represents true contamination (2.5\%) in simulations, and dotted horizontal line in top panel represents $5\%$ false positive rate. For this analysis we varied the contamination level in one individual from 0.5\% to 5.5\% while keeping contamination estimates for everyone else constant. We then analyzed the relatedness classification for this individual with all other individuals for power analysis.}
    \label{figS10:cnt}
\end{figure}
